---
title: "HW-2"
format: pdf
editor: visual
---

# Packages
 
## Question 1

```{r}
#| eval: FALSE
install.packages("aRtsy")
```

`install.packages()` downloads and installs a package on your computer. `library()` loads an installed package into the current R session.

\newpage

## Question 2

```{r}
library(aRtsy)
```

The Collatz conjecture starts with any postive integer `n`, if `n` is even, divide it by two; otherwise, multiply it by 3 and add 1. Repeats this process with the new `n` value. Eventually, `n` will reach to 1.

Let $f(n)$ be the next number obtained from $n$: $f(n)=\begin{cases}n/2,&\text{if }n/2 = 0,\\3n+1,&\text{if }n/2 = 1.\end{cases}$

\newpage

## Question 3

#### 3.a

```{r}
set.seed(7)
canvas_collatz(
  colors = c("blue"),
  n = 10
)
```

`canvas_collatz()` creates a plot of Collatz sequences using blue lines. `n = 10` tells it to choose 10 random starting integers.

#### 3.b

`canvas_collatz()` chooses 10 random starting integers, so it generates a different plot every time we run the code. This is troublesome in `.qmd` file because rendering again could change the plot, making the outcome hard to reproduce and compare. The `set.seed()` sets the same seed before generating random numbers gives the same outcome each time.

\newpage

## Question 4

```{r}
canvas_collatz(
  colors = c("blue"),
  n = 1:20
)
```

In question 3, `n = 10` tells `canvas_collatz()` to choose 10 random starting numbers. In question 4, we use a vector `n = 1:20`, which tells it to use the number 1 to 20 as staring numbers. This argument makes `canvas_collatz()` to generate the same plot each time we render. Since the staring numbers are fixed, including `set.seed()` is unnecessary: the seed would not change this plot.